Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-11 ind_files/02_BD_processes.tex
Minor notation changes in defn of Ito integral

The second integral in equation \eqref{ito_SDE_integral} is It\^o's `stochastic integral', and is to be interpreted in the following sense: Fix a time $T > 0$. Partition the interval $[0,T]$ into $n$ intervals of the form $[t_i,t_{i+1}]$ such that $0 = t_0 < t_1 < t_2 < \ldots < t_n = T$. Then, the (It\^o) stochastic integral from $0$ to $T$ can be thought of as:
\begin{equation*}
\int\limits_{0}^{T} G(s,X_s)dB_s \coloneqq \lim_{n \to \infty} \sum\limits_{i=1}^{n}G(t_i,X_{t_i})(B_{t_{i+1}}-B_{t_i})  
\end{equation*}
That is to say, it is obtained by making successively finer partitions of the form $[t_i,t_{i+1}]$, and then computing the `area of the rectangle' formed with $B_{t_{i+1}}-B_{t_i}$ and $G(t_i,X_{t_i})$ as sides. This should look similar to the classic Riemann integral, with the uniform width $t_{i+1}-t_i$ of the Riemann integral replaced by a random width corresponding to the random displacement of a Brownian particle during the uniform time interval $[t_i,t_{i+1}]$.

>>>>

The second integral in equation \eqref{ito_SDE_integral} is It\^o's `stochastic integral', and is to be interpreted in the following sense: Fix a time $T > 0$. For any $n\geq2$, let $\Pi_n = \{t_1,t_2,\ldots,t_n\}$ be a partition of the interval $[0,T]$. In other words, $\Pi_n$ divides $[0,T]$ into $n$ slices of the form $[t_i,t_{i+1}]$ such that $0 = t_0 < t_1 < t_2 < \ldots < t_n = T$. Then, the (It\^o) stochastic integral from $0$ to $T$ can be thought of as:
\begin{equation*}
\int\limits_{0}^{T} G(s,X_s)dB_s \coloneqq \lim_{n \to \infty} \sum\limits_{\Pi_n}G(t_i,X_{t_i})(B_{t_{i+1}}-B_{t_i})  
\end{equation*}
That is to say, it is obtained by making successively finer partitions of the form $[t_i,t_{i+1}]$, and then computing the `area of the rectangle' formed with $B_{t_{i+1}}-B_{t_i}$ and $G(t_i,X_{t_i})$ as sides. This should look similar to the classic Riemann integral, with the uniform width $t_{i+1}-t_i$ of the Riemann integral replaced by a random width corresponding to the random displacement of a Brownian particle during the uniform time interval $[t_i,t_{i+1}]$.
